### 2016-12-31 paper/evaluation.tex
update

As of December 30th 2016, our search criteria returned 615 subjects.
From the 615 downloaded projects, \Fix{we considered 312 projects that we
were able to compile and test. The others 277 could not be considered
because 39 were not Maven projects, 26 could not fetch all required
dependencies, 125 could not be compiled, and 87 could not execute the
tests.}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the 312 subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} illustrates the commands used in our
scripts to test each subject.  To avoid inflating the measured time,
we first compile the sources files (line 1) and later, we ran the
tests ignoring non-related tasks (line 3).  In addition, when we run a
subject's test suite, we operate Maven in offline mode to limit the
network access, avoiding any unnecessary package update as all
required \emph{jars} are available locally (line 2).  After the test
execution, we use a simple regular expression over the builder output
to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip, go, offline, P},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn dependency:go-offline
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Maven commands to test a subject:
    line 1 compiles all subject's source artifacts and make them
    available in a local repository (\ie, directory \emph{.m2} in the
    user's home directory); line 2 ensures all dependencies are
    resolved; line 3 runs the tests in offline mode ignoring javadoc
    generation.}
\end{figure}

>>>>

A Maven project may contain several submodules with multiple
\emph{pom.xml} files. We considered only projects with a
\emph{pom.xml} file located in the root directory.  As of December
30th 2016, our search criteria returned 615 subjects. From the 615
downloaded projects, 46 were not Maven projects, 25 were unable to fetch
all dependencies (\eg, due to the usage of a private library), and 128
were in an unstable revision. Our final set consists in 416 subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the 416 subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
to test each subject. The main loop (line 12) iterates over the list
of subjects and invokes the wrapper function \emph{run} to execute
Maven in separated steps (lines 14-16). To avoid inflating the
measured time, we first fetch all dependencies (line 14), compile the
source and test files (line 15) and later, we invoke Maven in offline
mode (line 16) to avoid package updates. In addition we randomly
selected 100 Maven logs to inspect and identify non-related tasks
(\eg, \emph{javadoc} generation and static analysis). We created a
list of plugins (lines 1-5) to ignore them during the test execution.
After the test execution, we use a simple regular expression over
the builder output to extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
}
\begin{lstlisting}[language=Python]
MAVEN_IGNORES = [
   "-Drat.skip=true", "-Dmaven.javadoc.skip=true",
   "-Djacoco.skip=true", "-Dcheckstyle.skip=true",
   "-Dfindbugs=true", "-Dcobertura.skip=true"
]

def run(cmds, opts=None):
   if opts not None:
      cmds.extend(opts)
   subprocess.call(cmds)

for subject in SUBJECTS:
   os.chdir(subject)
   run(["mvn", "dependency:go-offline"])
   run(["mvn", "clean", "install", "-DskipTests"])
   run(["mvn", "-o", "test"], MAVEN_IGNORES)
\end{lstlisting}
\caption{\label{fig:mvn-execution} Python script to evaluate the
    time cost of test suites. For each subject, we fetch all
    dependencies, compile the source and test files, and execute the
    tests in offline mode ignoring non-related tasks.}
\end{figure}
